\textbf{Teaching a machine to generate an artificial universe}

### 2020-08-20 paper.tex
update, rename report.tex to paper.tex

In the ACGAN framework each generated sample has a corresponding label $c \sim p_c$ and noise vector $z \sim p_z$ which 
make the generator create a sample $G(c, z)$. The discriminator $D$ gives probability distributions $P(S|X)$ and $P(C|X) 
= D(X)$ over the sources of the samples $S$ and class labels $C$. The objective function is made of two parts; the 
likelihood of a correct source $L_S$ and the log-likelihood of the correct class $L_C$

@@

\begin{figure}[!ht]%[hbt!]
\includegraphics[width=\columnwidth]{figures/diagrams/kernel_fig.png}
\centering
\caption{A histogram down-sampled with three kernels of size $k=\{1, 2, 4\}$ (from left to right).}
\label{fig:kernel_fig}
\end{figure}

@@

% The separate kernels cause averaging over different sized areas in the 2D case (volumes in the 3D case). By 
% construction the histograms are already sampling a volume at a fixed resolution for every distribution and so the kernel
% sizes give the same volume at different levels of resolution. A histogram from any distribution with each kernel 
% down-sampling will exhibit different scales of structure from the original unsampled histogram and this is shown in 
% Figure~\ref{fig:kernel_fig}. The ensembles drawn from each distribution are necessary to measure the difference in the 
% structure from the distributions that is not inherent in the individual variance of the images themselves. The latter 
% difference does not concern the distributions of the samples and is less important for the test of the generator capability.

>>>>

In the ACGAN framework each generated sample has a corresponding label $c \sim p_c$ and noise vector $\mathbf{z} \sim p_z$ which 
make the generator create a sample $G(c, \mathbf{z})$. The discriminator $D$ gives probability distributions $P(S|X)$ and $P(C|X) 
= D(X)$ over the sources of the samples $S$ and class labels $C$. The objective function is made of two parts; the 
likelihood of a correct source $L_S$ and the log-likelihood of the correct class $L_C$

@@

\begin{figure}[!ht]%[hbt!]
\includegraphics[width=\columnwidth]{figures/cubes/kernel_fig.png}
\centering
\caption{A histogram down-sampled with three kernels of size $k=\{1, 2, 4\}$ (from left to right).}
\label{fig:kernel_fig}
\end{figure}

@@

% The separate kernels cause averaging over different sized areas in the 2D case (volumes in the 3D case). By 
% construction the histograms are already sampling a volume at a fixed resolution for every distribution and so the kernel
% sizes give the same volume at different levels of resolution. A histogram from any distribution with each kernel 
% down-sampling will exhibit different scales of structure from the original unsampled histogram and this is shown in Figure~\ref{fig:kernel_fig}. The ensembles drawn from each distribution are necessary to measure the difference in the 
% structure from the distributions that is not inherent in the individual variance of the images themselves. The latter 
% difference does not concern the distributions of the samples and is less important for the test of the generator capability.
